---
title: "Coursera Data Science Captstone - Milestone Proyect"
output: html_notebook
autor: 'Carlos A. Gimenez'
date: '10/29/2017'
---

```{r, eval=FALSE, echo=FALSE}
library(tm)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

# Abstract

We analyze three corpora of US English text: Blogs, News & Twitter. The main objective of the study is to analize the text as a starting point for a future text predicting application.



# Getting Data and Exploring Basic Word Counts and Line Counts
```{r, eval=FALSE}
twitter <- readLines("./Coursera-Swiftkey/final/en_US/en_US.twitter.txt")
blogs <- readLines("./Coursera-Swiftkey/final/en_US/en_US.blogs.txt")
news <- readLines("./Coursera-Swiftkey/final/en_US/en_US.news.txt")
```

Get a sample of the files.
```{r}
data.sample <- (sample(twitter, length(twitter) * 0.05))
```

## Creating a subset corpus
```{r}
corpus <- VCorpus(VectorSource(data.sample))
# Elimino numeros
corpus <- tm_map(corpus, removeNumbers)
# Elimino puntuacion
corpus <- tm_map(corpus, removePunctuation, preserve_intra_word_dashes = TRUE)
# Elimino espacio es blanco
corpus <- tm_map(corpus, stripWhitespace)
# Convierto a lowercase
corpus <- tm_map(corpus, content_transformer(tolower))
# Elimino las stop words
corpus <- tm_map(corpus, content_transformer(removeWords), stopwords('english'))
```

# Exploratory Data Analysis

```{r}
NGramTokenizer1 <- function(x) unlist(lapply(NLP::ngrams(words(x), 1), paste, collapse =" "),
                                      use.names = FALSE)
NGramTokenizer2 <- function(x) unlist(lapply(NLP::ngrams(words(x), 2), paste, collapse =" "),
                                      use.names = FALSE)

NGramTokenizer3 <- function(x) unlist(lapply(NLP::ngrams(words(x), 3), paste, collapse =" "),
                                      use.names = FALSE)

ngram.1 <- TermDocumentMatrix(corpus, control=list(tokenize=NGramTokenizer1))
ngram.2 <- TermDocumentMatrix(corpus, control=list(tokenize=NGramTokenizer2))
ngram.3 <- TermDocumentMatrix(corpus, control=list(tokenize=NGramTokenizer3))
```

```{r}
saveRDS(ngram.1, 'ngram1.rds')
saveRDS(ngram.2, 'ngram2.rds')
saveRDS(ngram.3, 'ngram3.rds')
```

```{r}
ngram.1 <- readRDS('ngram1.rds')
ngram.2 <- readRDS('ngram2.rds')
ngram.3 <- readRDS('ngram3.rds')
```


## Unigram Analysis
As we can see in the follow wordcloud, the most common words are "just", "get", "love", "will" and others.
```{r, warning=FALSE}
library(wordcloud)

w <- findFreqTerms(ngram.1, lowfreq = 200)
wf <- rowSums(as.matrix(ngram.1[w,]))
wf <- data.frame(unigram=names(wf), frequency=wf)
df <- data.frame(wf[,c('unigram','frequency')], row.names = NULL)
wordcloud(df$unigram, df$frequency, min.freq=200, colors=brewer.pal(6, "Dark2")) 
```


## Two-gram Analysis
The most frequent two-gram are "cant wait", "dont know" and "can get".
```{r}
require(ggplot2)
w <- findFreqTerms(ngram.2, lowfreq = 100)
wf <- rowSums(as.matrix(ngram.2[w,]))
df <- data.frame(word=names(wf), frequency=wf, row.names = NULL)

ggplot(df[1:15,], aes(x=reorder(word, frequency), y=frequency)) +
geom_bar(stat = "identity", position = "dodge", fill = "darkred") + 
coord_flip() +
xlab("Bi-gram words") + ylab("Sample Frequency") +
ggtitle('Most Common Bi-grams')
```

## Three-gram Analysis

```{r}
require(ggplot2)
w <- findFreqTerms(ngram.3, lowfreq = 30)
wf <- rowSums(as.matrix(ngram.3[w,]))
df <- data.frame(word=names(wf), frequency=wf, row.names = NULL)

ggplot(df[1:15,], aes(x=reorder(word, frequency), y=frequency)) +
geom_bar(stat = "identity", position = "dodge", fill = "darkred") + 
coord_flip() +
xlab("Tri-gram words") + ylab("Sample Frequency") +
ggtitle('Most Common Tri-grams')
```



# Other Questions:

Q: How do you evaluate how many of the words come from foreign languages?

A: We can use dictionaries. 

Q: Can you think of a way to increase the coverage – identifying words that may not be in the corpora or using a smaller number of words in the dictionary to cover the same number of phrases?

A: We should use synonyms to reduce the overall number of words



